Notes on @nolan2010computing

### 2019-11-02 Rmd/discussion.Rmd
updated methods

Benefits of our framework

@@

>>>>

Benefits of our framework include enhanced

@@

### Areas for improvement

1. reproducible research best practices

One shortcoming of our initial framework was the relative lack of emphasis on best practices for computational reproducibility. This is one area that we would like to rectify in future iterations. The University of Wisconsin-Madison has periodically offered a semester course in best practices for computationally reproducible research. We especially see version control systems, such as Git and Github, as essential tools for the modern data scientist.

### 2019-11-02 Rmd/methods.Rmd
updated methods

>>>>

### Broaden statistical computing to include emerging areas

Our framework broadens statistical computing by including the emerging areas of
social media data analysis, sentiment analysis, and topic modeling. 
Both of our students used Twitter tweets, which we accessed through a Twitter 
streaming API.

Our computational system for acquiring tweets involved several steps. We interacted with the API via the R package `twitteR` [@twitteR]. We used the free Twitter streaming API that gave us access to approximately one percent stream of all tweets during the specified query time period. To ensure that we collected tweets continuously, we used the linux tool `crontab` to execute our R script every five minutes. Each execution of the R script performed a single streaming API query, lasting five minutes. Twitter's streaming API, at the time of our data collection, enforced rate limits on the frequency and duration of queries.

### deepen computational reasoning skills

Our framework, and the projects developed under it, encourage students to deepen 
computational reasoning skills in several ways. First, they work with a variety of 
internet-based data to answer research questions. In the two example cases, our 
students collected tweets over time and gathered complementary data from other 
resources, including daily closing prices of stock market indexes.

Second, the students worked with a variety of data structures. 
The Twitter streaming 
API returns tweets as JSON files. Because distinct Twitter users may provide 
different pieces of profile information, there is variability in the structure of 
each tweet's JSON entry. Students needed to recognize this, and write code that 
accommodated these variations in tweet data structure.

### combine computational topics with data analysis in the practice of statistics
